\systemnamenospace: Head Orientation Based Selection\\in Physical Spaces

### 2014-08-13 doc/sui14/iteration1.tex
update participant number & demographics. TBC

\subsection{Method}
We deployed 10 wireless nodes in an indoor environment (Figure~\ref{fig:targeting-study-layout}). Each of them has a number as ID and a letter representing the name. We recruited 14 participants from our institution \changes{from email invitations} for this study. 13 had never used Google Glass before, so we offered a tutorial before the experiment in order to introduce the device. Four participants wore prescription glasses, which makes Glass more cumbersome to use and adjust and may have affected their task performance. In this study, the IR LED was fixed and not repositionable as shown in Figure~\ref{fig:glass}.

@@

\changes{Most participants walked one or two steps during each task. In the survey we asked \studyquote{When you have multiple candidate targets within sight, which method for selecting between did you use?} (multiple choice), among 16 participates, X\% chose {\em adjust head so that only one candidate is signaled}, Y\% chose {\em walk closer to the candidate for a better result}, and only Z\% chose {\em tap (to enter refinement stage) and then choose between list}. \sean{will update numbers and add a few sentences here.}}
As for the qualitative feedback, 11 out of 14 participants preferred IR selection over list mode (two preferred list, one was undecided). While both interfaces were judged similarly on overall ease of connecting, IR selection was perceived to be more direct and \changes{pleasant}. One user noted benefit of {\em IR selection}  \studyquote{allowing users to focus on the targeted objects instead of the screen}. \achal{This seems rather weak... Don't really need all the quotes.} One subject called it \studyquote{natural to interact with things just by looking at them}. Another mentioned that \studyquote{it's really convenient that what I'm looking at is what I'm targeting}.

>>>>

\subsection{Method}
We deployed 10 wireless nodes in an indoor environment (Figure~\ref{fig:targeting-study-layout}). Each of them has a number as ID and a letter representing the name. We recruited \changes{16} participants from our institution \changes{from email invitations} for this study \changes{(8 males, 6 females)} And figure X shows their department distribution. \sean{will calculate later. shall we use a pie chart?}  \changes{14} had never used Google Glass before, so we offered a tutorial before the experiment in order to introduce the device. Four participants wore prescription glasses, which makes Glass more cumbersome to use and adjust and may have affected their task performance. In this study, the IR LED was fixed and not repositionable as shown in Figure~\ref{fig:glass}.

@@

\changes{Most participants walked one or two steps during each task. In the survey we asked \studyquote{When you have multiple candidate targets within sight, which method for selecting between did you use?} (multiple choice), among 16 participates, X\% chose {\em adjust head so that only one candidate is signaled}, Y\% chose {\em walk closer to the candidate for a better result}, and only Z\% chose {\em tap (to enter refinement stage) and then choose between list}. \sean{will update numbers and add a few sentences here.}}

As for the qualitative feedback, 11 out of 14 participants preferred IR selection over list mode (two preferred list, one was undecided). While both interfaces were judged similarly on overall ease of connecting, IR selection was perceived to be more direct and \changes{pleasant}. One user noted benefit of {\em IR selection}  \studyquote{allowing users to focus on the targeted objects instead of the screen}. \achal{This seems rather weak... Don't really need all the quotes.} One subject called it \studyquote{natural to interact with things just by looking at them}. Another mentioned that \studyquote{it's really convenient that what I'm looking at is what I'm targeting}.
